ABC - HTW Fits

### 2023-11-29 Model/abc_fit.qmd
alt run for consistency

# store all models in list and save to data/model_cache
model_cache <- tibble:lst(
  abc_results_varied_exam = abc_results_varied_exam,
  abc_results_varied_alt_exam = abc_results_varied_alt_exam,
  abc_results_varied_alm = abc_results_varied_alm,
  abc_results_constant_alm = abc_results_constant_alm,
  abc_results_constant_exam = abc_results_constant_exam,
  abc_results_constant_alt_exam = abc_results_constant_alt_exam
)

>>>>

# store all models in list and save to data/model_cache
model_cache <- list(
  abc_results_varied_exam = abc_results_varied_exam,
  abc_results_varied_alt_exam = abc_results_varied_alt_exam,
  abc_results_varied_alm = abc_results_varied_alm,
  abc_results_constant_alm = abc_results_constant_alm,
  abc_results_constant_exam = abc_results_constant_exam,
  abc_results_constant_alt_exam = abc_results_constant_alt_exam
)
